Understanding meta-analysis through data simulation with application to power analysis

### 2023-09-26 documents/paper/paper.Rmd
final fix

keywords          : "meta-analysis, monte carlo simulations, power analysis"
wordcount         : 7869
bibliography      : "../files/references.bib"
floatsintext      : yes
figsintext        : yes
linenumbers       : "`r params$linenumbers`"
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
numbersections    : false
nocite: |
  @r-lang
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1,footnotesize}}
  - \usepackage{float}
  - \usepackage{orcidlink}
  - \newcommand{\rev}[1]{\textcolor{red}{#1}}
documentclass     : "apa6"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
params: 
  linenumbers: "yes"
  finalsection: TRUE
---

@@

```{r packages, include=FALSE}
library(papaja)
library(metafor)
library(dplyr)
library(tidyr)
library(kableExtra)
library(here)
library(latex2exp)
library(ltxplot)

rcit <- sprintf("(version %s.%s; R Core Team, %s)", R.version$major, R.version$minor, R.version$year)
ltxplot::load_theme_ltx()
devtools::load_all()
seed <- 2023 # general seed for all simulations
```

>>>>

keywords          : "meta-analysis, monte carlo simulations, power analysis"
wordcount         : 7869
bibliography      : "../files/references.bib"
floatsintext      : yes
figsintext        : yes
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
numbersections    : false
nocite: |
  @r-lang
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1,footnotesize}}
  - \usepackage{float}
  - \usepackage{orcidlink}
  - \newcommand{\rev}[1]{\textcolor{red}{#1}}
documentclass     : "apa6"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
---

@@

```{r packages, include=FALSE}
library(papaja)
library(metafor)
library(dplyr)
library(tidyr)
library(kableExtra)
library(here)
library(latex2exp)
library(ltxplot)
devtools::load_all()

rcit <- sprintf("(version %s.%s; R Core Team, %s)", R.version$major, R.version$minor, R.version$year)
ltxplot::load_theme_ltx()
seed <- 2023 # general seed for all simulations
```
